---
title: "Part One Explore"
output: html_notebook
---

```{r}
library(tidyverse)
```



#### Hypothesis confirmation
It’s possible to divide data analysis into two camps: hypothesis generation and hypothesis confirmation (sometimes called confirmatory analysis). The focus of this book is unabashedly on hypothesis generation, or data exploration. Here you’ll look deeply at the data and, in combination with your subject knowledge, generate many interesting hypotheses to help explain why the data behaves the way it does. You evaluate the hypotheses informally, using your scepticism to challenge the data in multiple ways.

The complement of hypothesis generation is hypothesis confirmation. Hypothesis confirmation is hard for two reasons:

You need a precise mathematical model in order to generate falsifiable predictions. This often requires considerable statistical sophistication.

You can only use an observation once to confirm a hypothesis. As soon as you use it more than once you’re back to doing exploratory analysis. This means to do hypothesis confirmation you need to “preregister” (write out in advance) your analysis plan, and not deviate from it even when you have seen the data. We’ll talk a little about some strategies you can use to make this easier in modelling.

It’s common to think about modelling as a tool for hypothesis confirmation, and visualisation as a tool for hypothesis generation. But that’s a false dichotomy: models are often used for exploration, and with a little care you can use visualisation for confirmation. The key difference is how often do you look at each observation: if you look only once, it’s confirmation; if you look more than once, it’s exploration. ####


```{r}
library(ggplot2)
ggplot(mpg, aes(x = displ, y = hwy)) + geom_point(aes(colour = class))
```









































